%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Projects}



%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Graph Neural Networks applied to mathematics} %  Architecture
    {Thesis project for BSc} % Project
    {Milan, Italy} % Location
    {Sep. 2023 - Sep. 2024} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Reasearch on Applications of graph neural network to partial differential equations}
        \item {Implementation of Graph Neural Network model using HydraGNN package and tensorflow geometric, developed by Oak Ridge National Laboratory (ORNL). Definition of the model structure, imput conversion and hyperparameter tuning.}
        \item {Generation of the dataset using Finite Element Methods and FEM software to recreate a topology optimization problem as a case study}
        \item {Testing and validation of the obtained model and analysis of the obtained results.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Java, C and VHDL} %  Architecture
    {Final projects for MSc} % Project
    {Milan, Italy} % Location
    {Sep. 2020 - Sep. 2021} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Digital version for the board game Maestri Del Rinascimento}
            \begin{itemize}
                \item {Implementation in Java of a board game with a client-server architecture}
                \item {MVC Pattern and asynchronous requests to the server}
                \item {Collaboration tools such as git and software life cycle handled with Maven}
            \end{itemize}
        \item {Algorithms and data structures project in C}
            \begin{itemize}
                \item {Study and implementation of different algorithms such as Dijkstra's}
                \item {Memory efficient and time efficient optimization}
            \end{itemize}
        \item {VHDL Design, implementation and report of a board component included and tested in a bigger architecture}
      \end{cvitems}
    }

%---------------------------------------------------------
 \cventry
    {Robotics, Neural networks, computer vision and sensor systems} % Architecture
    {Other projects during my MSc} % Project
    {Milan, Italy} % Location
    {Sep. 2020 - Sep. 2021} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Robot odometry calculation and location (SLAM) using ROS and bag of real data from encoders and sensors for Robotics course (Grade 30/30)}
        \item {Elaboration of computer vision dataset with multiplane homographies and benchmarking of different alghoritms with OpenCV (Grade 27/30)}
        \item {Design and implementation of two different Neural Network architectures for image classification and time series analysis (Grade 29/30)}
        \item {Multiple projects using STM32 microcontroller, multiple sensors and other circuit components such as capacitors (Grade 26/30)}
      \end{cvitems}
      %\begin{cvsubentries}
      %  \cvsubentry{}{KNOX(Solution for Enterprise Mobile Security) Penetration Testing}{Sep. 2013}{}
      %  \cvsubentry{}{Smart TV Penetration Testing}{Mar. 2011 - Oct. 2011}{}
      %\end{cvsubentries}
    }

%---------------------------------------------------------
\end{cventries}
